Oregon average visit rates for saba & asthma emergency data set for metrapolitan per month

### 2018-05-30 r_scripts/analysis/oregon_asthma_er_saba_msa_count_results.Rmd
modified and renamed part c to just import saved count by msa and month datasets rather than recreate whole thing.

```{r load ER data set and zip smoke, message=FALSE, warning=FALSE}

@@

```{r saba, message=FALSE, warning=FALSE}
pharmacy_df <- saba_df %>%
  mutate(age = 2013 - year) %>%
  mutate(age_cat = case_when(age < 15 ~ "Age < 15",
                                age >= 15 & age < 65 ~ "Age 15-65",
                                age >= 65 ~ "Age > 65"),
              metroarea = case_when(MSA == 13460 ~ "Bend-Redmond",
                                MSA == 18700 ~ "Corvallis",
                                MSA == 21660 ~ "Eugene-Springfield",
                                MSA == 32780 ~ "Medford",
                                MSA == 38900 ~ "Portland-Vancouver-Beaverton",
                                MSA == 41420 ~ "Salem")) %>%
  mutate(month = month(fromdate)) %>%
  inner_join(or_msa_pop[,c(1,3)], by = "MSA") # 352,150 visits, 131,725 people

@@

@@

summary_table_pharmacy$group <- factor(paste0(summary_table_pharmacy$month, summary_table_pharmacy$NAME))
X <- model.matrix(~ 0 + group, data=summary_table_pharmacy)
# colnames(X)

fit <- glm(n_visit ~ 0 + month*NAME, offset = log(POPESTIMATE2013), family = poisson, data = summary_table_pharmacy)
# summary(fit)

fit_group <- glm(n_visit ~ 0 + group, offset = log(POPESTIMATE2013), family = poisson, data = summary_table_pharmacy)
# summary(fit_group)

@@

# change the numeric variable as factor
summary_table_er$month <- as.factor(summary_table_er$month)
summary_table_er$MSA <- as.factor(summary_table_er$MSA)

summary_table_er$group <- factor(paste0(summary_table_er$month, summary_table_er$NAME))
X <- model.matrix(~ 0 + group, data=summary_table_er)
# colnames(X)

fit <- glm(n_visit ~ 0 + month*NAME, offset = log(POPESTIMATE2013), family = poisson, data = summary_table_er)
# summary(fit)

fit_group <- glm(n_visit ~ 0 + group, offset = log(POPESTIMATE2013), family = poisson, data = summary_table_er)
# summary(fit_group)

>>>>

*Ryan: Setting Eval to False and importing timeseries rather than recreating.*
```{r load ER data set and zip smoke, message=FALSE, warning=FALSE, eval=F}

@@

```{r saba, message=FALSE, warning=FALSE, eval=F}
pharmacy_df <- saba_df %>%
  mutate(age = 2013 - year) %>%
  mutate(age_cat = case_when(age < 15 ~ "Age < 15",
                                age >= 15 & age < 65 ~ "Age 15-65",
                                age >= 65 ~ "Age > 65"),
              metroarea = case_when(MSA == 13460 ~ "Bend-Redmond",
                                MSA == 18700 ~ "Corvallis",
                                MSA == 21660 ~ "Eugene-Springfield",
                                MSA == 32780 ~ "Medford",
                                MSA == 38900 ~ "Portland-Vancouver-Beaverton",
                                MSA == 41420 ~ "Salem")) %>%
  mutate(month = month(fromdate)) %>%
  inner_join(or_msa_pop[,c(1,3)], by = "MSA") # 352,150 visits, 131,725 people

@@

```{r read_counts}
saba_count <- read_csv("../../data/health/saba_month_counts.csv")
ed_count <- read_csv("../../data/health/asthma_er_month_counts.csv")
```

@@

```{r message=FALSE, warning=FALSE}
saba_count
saba_count$group <- factor(paste0(saba_count$month, saba_count$NAME))
X <- model.matrix(~ 0 + group, data=saba_count)
# colnames(X)

fit <- glm(n_saba ~ 0 + month*NAME, offset = log(POPESTIMATE2013), 
           family = poisson, data = saba_count)
# summary(fit)

fit_group <- glm(n_saba ~ 0 + group, offset = log(POPESTIMATE2013), 
                 family = poisson, data = saba_count)
# summary(fit_group)

@@

# change the numeric variable as factor
ed_count$month <- as.factor(ed_count$month)
ed_count$MSA <- as.factor(ed_count$MSA)

ed_count$group <- factor(paste0(ed_count$month, ed_count$NAME))
X <- model.matrix(~ 0 + group, data=ed_count)
# colnames(X)

fit <- glm(n_ed ~ 0 + month*NAME, 
           offset = log(POPESTIMATE2013), family = poisson, 
           data = ed_count)
# summary(fit)

fit_group <- glm(n_ed ~ 0 + group, offset = log(POPESTIMATE2013), 
                 family = poisson, data = summary_table_er)
# summary(fit_group)
